Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2023-01-02 paper/main.tex
working on clustering figures, corrected label errors
added clustering scatterplot figure

% figure: feature clustering vs. accuracy, feature clustering vs. temporal clustering

>>>>

% figure: feature clustering vs. accuracy, feature clustering vs. temporal clustering
\begin{figure}[tp] \centering
\includegraphics[width=\textwidth]{figures/feature_clustering_vs_accuracy_and_contiguity}

\caption{\textbf{Interactions between feature clustering, recall probability,
and contiguity.} \textbf{A.} Recall probability versus feature clustering
scores for order manipulation (early) lists. \textbf{B.} Recall probability
versus feature clustering for randomly ordered (late) lists. \textbf{C.} Recall
probability on late lists versus feature clustering on early lists. \textbf{D.}
Recall probability on early lists versus feature clustering on late lists.
\textbf{E.} Temporal clustering scores (contiguity) versus feature clustering
scores on early lists. \textbf{F.} Temporal clustering scores versus feature
clustering scores on late lists. \textbf{G.} Temporal clustering scores on late
lists versus feature clustering scores on early lists. \textbf{H.} Temporal
clustering scores on early lists versus feature clustering scores on late
lists. \textbf{All panels.} Each dot in the main scatterplots denotes the
average scores for one participant. The colored regression lines are computed
across participants. The inset displays condition-averaged results, where each
dot reflects a single condition and the regression line is computed across
experimental conditions. All error ribbons denote bootstrap-estimated 95\%
confidence intervals.} \label{fig:clustering-scatterplots}

\end{figure}
